### 2009-04-01 docs/eos_notes/eos_notes.tex
finished the list of eos calls in advance.f90

\section{EOS Calls}
\section{Temperature Usage}

>>>>

\section{EOS Calls}
\subsection{Initialization}
\subsection{{\tt advance\_timestep}}
\begin{description}
\item[Step 1.] {\em Define the average expansion at time $t^\nph$ and the new $w_0.$}
\begin{itemize}
\item In {\tt makePfromRhoH}, we compute a thermodynamic $p^n$ for the volume discrepancy 
term using $(\rho,h,X)^n$.
\end{itemize}
\item[Step 2.] {\em Construct the provisional edge-based advective velocity, $\uadvone.$}
\item[Step 3.] {\em React the full state and base state through the first time interval 
of $\dt/2.$}
\begin{itemize}
\item In {\tt react\_state} $\rightarrow$ {\tt burner}, we compute $c_p$ and $\xi_k$ 
for inputs to {\tt VODE} using $(\rho,T,X)^n$.
\item In {\tt react\_state}, we compute $T^{(1)}$ using $(\rho,h,X)^{(1)}$ 
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(1)}$ and $p_0^n$ (if {\tt use\_tfromp}=T).
\item In {\tt make\_gamma}, we compute $\Gamma_1$ using $(\rho,X)^{(1)}$ and $p_0^n$.
\end{itemize}
\item[Step 4.] {\em Advect the base state, then the full state, through a time interval 
of $\dt.$}\\
If {\tt use\_thermal\_diffusion} = T:
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$.
\item In {\tt enthalpy\_advance} $\rightarrow$ {\tt update\_scal}, we compute $h$ above
the {\tt base\_cutoff\_density} using $(\rho,X)^{(2),*}$ and $p_0^{n+1,*}$.
\item In {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$.
\item In {\tt thermal\_conduct}, we compute $T^{(2),*}$ using $(\rho,h,X)^{(2),*}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2),*}$ and $p_0^{n+1,*}$ (if {\tt use\_tfromp}=T).
\end{itemize}
If {\tt use\_thermal\_diffusion} = F:
\begin{itemize}
\item In {\tt enthalpy\_advance} $\rightarrow$ {\tt update\_scal}, we compute $h$ above
the {\tt base\_cutoff\_density} using $(\rho,X)^{(2),*}$ and $p_0^{n+1,*}$.
\item In {\tt enthalpy\_advance}, we compute $T^{(2),*}$ using $(\rho,h,X)^{(2),*}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2),*}$ and $p_0^{n+1,*}$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 5.] {\em React the full state through a second time interval of $\dt/2.$}
\begin{itemize}
\item In {\tt react\_state} $\rightarrow$ {\tt burner}, we compute $c_p$ and $\xi_k$ 
for inputs to {\tt VODE} using $(\rho,T,X)^{(2),*}$.
\item In {\tt react\_state}, we compute $T^{n+1,*}$ using $(\rho,h,X)^{n+1,*}$ 
(if {\tt use\_tfromp}=F) or $(\rho,X)^{n+1,*}$ and $p_0^{n+1,*}$ (if {\tt use\_tfromp}=T).
\item In {\tt make\_gamma}, we compute $\Gamma_1$ using $(\rho,X)^{n+1,*}$ and $p_0^{n+1,*}$.
\end{itemize}
\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{n+1,*}$.
\item In {\tt make\_S}, we compute thermodynamic variables using $(\rho,T,X)^{n+1,*}$.
\item In {\tt makePfromRhoH}, we compute a thermodynamic $p^{n+1,*}$ for the volume 
discrepancy term using $(\rho,h,X)^{n+1,*}$.
\end{itemize}
\item[Step 7.] {\em Construct the final edge-based advective velocity, $\uadvtwo.$}
\item[Step 8.] {\em Advect the base state, then the full state, through a time interval 
of $\dt.$}\\
If {\tt use\_thermal\_diffusion} = T:
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$.
\item In {\tt enthalpy\_advance} $\rightarrow$ {\tt update\_scal}, we compute $h$ above
the {\tt base\_cutoff\_density} using $(\rho,X)^{(2)}$ and $p_0^{n+1}$.
\item In {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$ and $(\rho,T,X)^{(2),*}$.
\item In {\tt thermal\_conduct}, we compute $T^{(2)}$ using $(\rho,h,X)^{(2)}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2)}$ and $p_0^{n+1}$ (if {\tt use\_tfromp}=T).
\end{itemize}
If {\tt use\_thermal\_diffusion} = F:
\begin{itemize}
\item In {\tt enthalpy\_advance} $\rightarrow$ {\tt update\_scal}, we compute $h$ above
the {\tt base\_cutoff\_density} using $(\rho,X)^{(2)}$ and $p_0^{n+1}$.
\item In {\tt enthalpy\_advance}, we compute $T^{(2)}$ using $(\rho,h,X)^{(2)}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2)}$ and $p_0^{n+1}$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 9.] {\em React the full state and base state through a second time interval 
of $\dt/2.$}
\begin{itemize}
\item In {\tt react\_state} $\rightarrow$ {\tt burner}, we compute $c_p$ and $\xi_k$ 
for inputs to {\tt VODE} using $(\rho,T,X)^{(2)}$.
\item In {\tt react\_state}, we compute $T^{n+1}$ using $(\rho,h,X)^{n+1}$ 
(if {\tt use\_tfromp}=F) or $(\rho,X)^{n+1}$ and $p_0^{n+1}$ (if {\tt use\_tfromp}=T).
\item In {\tt make\_gamma}, we compute $\Gamma_1$ using $(\rho,X)^{n+1}$ and $p_0^{n+1}$.
\end{itemize}
\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{n+1}$.
\item In {\tt make\_S}, we compute thermodynamic variables using $(\rho,T,X)^{n+1}$.
\end{itemize}
\item[Step 11.] {\em Update the velocity.}
\item[Step 12.] {\em Compute a new $\dt.$}
\end{description}
\subsection{{\tt make\_plotfile}}
\section{Temperature Usage}
\subsection{{\tt advance\_timestep}}
\begin{description}
\item[Step 1.] {\em Define the average expansion at time $t^\nph$ and the new $w_0.$}
\item[Step 2.] {\em Construct the provisional edge-based advective velocity, $\uadvone.$}
\item[Step 3.] {\em React the full state and base state through the first time interval 
of $\dt/2.$}
\begin{itemize}
\item In {\tt react\_state} $\rightarrow$ {\tt burner}, we compute $c_p$ and $\xi_k$ 
for inputs to {\tt VODE} using $(\rho,T,X)^n$.
\item In {\tt react\_state}, we compute $T^{(1)}$ using $(\rho,h,X)^{(1)}$ 
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(1)}$ and $p_0^n$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 4.] {\em Advect the base state, then the full state, through a time interval 
of $\dt.$}\\
If {\tt use\_thermal\_diffusion} = T:
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$.
\item In {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$.
\item In {\tt thermal\_conduct}, we compute $T^{(2),*}$ using $(\rho,h,X)^{(2),*}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2),*}$ and $p_0^{n+1,*}$ (if {\tt use\_tfromp}=T).
\end{itemize}
If {\tt use\_thermal\_diffusion} = F:
\begin{itemize}
\item In {\tt enthalpy\_advance}, we compute $T^{(2),*}$ using $(\rho,h,X)^{(2),*}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2),*}$ and $p_0^{n+1,*}$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 5.] {\em React the full state through a second time interval of $\dt/2.$}
\begin{itemize}
\item In {\tt react\_state} $\rightarrow$ {\tt burner}, we compute $c_p$ and $\xi_k$ 
for inputs to {\tt VODE} using $(\rho,T,X)^{(2),*}$.
\item In {\tt react\_state}, we compute $T^{n+1,*}$ using $(\rho,h,X)^{n+1,*}$ 
(if {\tt use\_tfromp}=F) or $(\rho,X)^{n+1,*}$ and $p_0^{n+1,*}$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{n+1,*}$.
\item In {\tt make\_S}, we compute thermodynamic variables using $(\rho,T,X)^{n+1,*}$.
\end{itemize}
\item[Step 7.] {\em Construct the final edge-based advective velocity, $\uadvtwo.$}
\item[Step 8.] {\em Advect the base state, then the full state, through a time interval 
of $\dt.$}\\
If {\tt use\_thermal\_diffusion} = T:
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$.
\item In {\tt thermal\_conduct}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{(1)}$ and $(\rho,T,X)^{(2),*}$.
\item In {\tt thermal\_conduct}, we compute $T^{(2)}$ using $(\rho,h,X)^{(2)}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2)}$ and $p_0^{n+1}$ (if {\tt use\_tfromp}=T).
\end{itemize}
If {\tt use\_thermal\_diffusion} = F:
\begin{itemize}
\item In {\tt enthalpy\_advance}, we compute $T^{(2)}$ using $(\rho,h,X)^{(2)}$
(if {\tt use\_tfromp}=F) or $(\rho,X)^{(2)}$ and $p_0^{n+1}$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 9.] {\em React the full state and base state through a second time interval 
of $\dt/2.$}
\begin{itemize}
\item In {\tt react\_state} $\rightarrow$ {\tt burner}, we compute $c_p$ and $\xi_k$ 
for inputs to {\tt VODE} using $(\rho,T,X)^{(2)}$.
\item In {\tt react\_state}, we compute $T^{n+1}$ using $(\rho,h,X)^{n+1}$ 
(if {\tt use\_tfromp}=F) or $(\rho,X)^{n+1}$ and $p_0^{n+1}$ (if {\tt use\_tfromp}=T).
\end{itemize}
\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}
\begin{itemize}
\item In {\tt make\_explicit\_thermal}, we compute the coefficients for 
$\nabla\cdot(\kth/c_p)\nabla h + \cdots$ using $(\rho,T,X)^{n+1}$.
\item In {\tt make\_S}, we compute thermodynamic variables using $(\rho,T,X)^{n+1}$.
\end{itemize}
\item[Step 11.] {\em Update the velocity.}
\item[Step 12.] {\em Compute a new $\dt.$}
\end{description}
